---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# allometrydata

Allometry data storage for the BWG.

## Installation

```{r, eval = FALSE}
devtools::install_github("SrivastavaLab/allometrydata")
```

## Data Access

Allometry data can be accessed directly using this package.

Access the most recent version on GitHub.

```{r, eval = FALSE}
allometrydata::alldata()
```

List the versions available online:

```{r}
allometrydata::alldata_versions(local = FALSE)
```

List the versions available on your computer:

```{r}
allometrydata::alldata_versions()
```

For help:

```{r}
?allometrydata::alldata()
```

## Data Versions

See [releases](https://github.com/SrivastavaLab/allometrydata/releases) for the
most recent versions of the data.

## Data Update

Data may be updated by an administrator by connecting to your local Dropbox
folder: `CommunityAnalysis/Allometry`. The function `update_data` will
compile any new XLS files from the Allometry folder with the most recent version
of the data on GitHub. The dataset is saved locally and can be uploaded as a new
data release.

Data updates keep the original data largely as is, with a few exceptions:

1) Only the following expected columns are retained: `bwg_name`, `name`,
`length_mm`, `wet_mass_mg`, `dry_mass_mg`, `length_measured_as`,
`number_of_individuals`, `stage`, `size_category`, `instar_number`
2) Two columns are added to better describe the data. `file` gives the filename
from which the line of data came. `type` distinguishes between measurements
gathered in the field (`field_measurement`) and entries used to define a size
category by giving a corresponding length (`category_definition`). Notably, data
that fall into the `category_definition` type do not include biomass
measurements as they do not represent an actual measurement.
3) Any blanks are converted to `NA`
